\label{sec:contributions}
\textbf{Tom Brown, Ben Mann, Prafulla Dhariwal, Dario Amodei, Nick Ryder, Daniel M Ziegler, and Jeffrey Wu} implemented the large-scale models, training infrastructure, and model-parallel strategies.

\textbf{Tom Brown, Dario Amodei, Ben Mann, and Nick Ryder} conducted pre-training experiments.

\textbf{Ben Mann and Alec Radford} collected, filtered, deduplicated, and conducted overlap analysis on the training data.

\textbf{Melanie Subbiah, Ben Mann, Dario Amodei, Jared Kaplan, Sam McCandlish, Tom Brown, Tom Henighan, and Girish Sastry} implemented the downstream tasks and the software framework for supporting them, including creation of synthetic tasks.

\textbf{Jared Kaplan and Sam McCandlish} initially predicted that a giant language model should show continued gains, and applied scaling laws to help predict and guide model and data scaling decisions for the research.

\textbf{Ben Mann} implemented sampling without replacement during training.

\textbf{Alec Radford} originally demonstrated few-shot learning occurs in language models.

\textbf{Jared Kaplan and Sam McCandlish} showed that larger models learn more quickly in-context, and systematically studied in-context learning curves, task prompting, and evaluation methods.

\textbf{Prafulla Dhariwal} implemented an early version of the codebase, and developed the memory optimizations for fully half-precision training.

\textbf{Rewon Child and Mark Chen} developed an early version of our model-parallel strategy.

\textbf{Rewon Child and Scott Gray} contributed the sparse transformer.

\textbf{Aditya Ramesh} experimented with loss scaling strategies for pretraining.

\textbf{Melanie Subbiah and Arvind Neelakantan} implemented, experimented with, and tested beam search.

\textbf{Pranav Shyam} worked on SuperGLUE and assisted with connections to few-shot learning and meta-learning literature.

\textbf{Sandhini Agarwal} conducted the fairness and representation analysis.

\textbf{Girish Sastry and Amanda Askell} conducted the human evaluations of the model.

\textbf{Ariel Herbert-Voss} conducted the threat analysis of malicious use.

\textbf{Gretchen Krueger} edited and red-teamed the policy sections of the paper.

\textbf{Benjamin Chess, Clemens Winter, Eric Sigler, Christopher Hesse, Mateusz Litwin, and Christopher Berner} optimized OpenAI’s clusters to run the largest models efficiently.

\textbf{Scott Gray} developed fast GPU kernels used during training.

\textbf{Jack Clark} led the analysis of ethical impacts — fairness and representation, human assessments of the model, and broader impacts analysis, and advised Gretchen, Amanda, Girish, Sandhini, and Ariel on their work.

\textbf{Dario Amodei, Alec Radford, Tom Brown, Sam McCandlish, Nick Ryder, Jared Kaplan, Sandhini Agarwal, Amanda Askell, Girish Sastry, and Jack Clark} wrote the paper.

\textbf{Sam McCandlish} led the analysis of model scaling, and advised Tom Henighan and Jared Kaplan on their work.

\textbf{Alec Radford} advised the project from an NLP perspective, suggested tasks, put the results in context, and demonstrated the benefit of weight decay for training.

\textbf{Ilya Sutskever} was an early advocate for scaling large generative likelihood models, and advised Pranav, Prafulla, Rewon, Alec, and Aditya on their work.

\textbf{Dario Amodei} designed and led the research.
