\input{tables/reading_comprehension.tex}
\input{graphs/coqa.tex}
Next we evaluate GPT-3 on the task of reading comprehension. We use a suite of 5 datasets including abstractive, multiple choice, and span based answer formats in both dialog and single question settings. We observe a wide spread in GPT-3's performance across these datasets suggestive of varying capability with different answer formats. In general we observe GPT-3 is on par with initial baselines and early results trained using contextual representations on each respective dataset.

GPT-3 performs best (within 3 points of the human baseline) on CoQA \cite{reddy2019coqa} a free-form conversational dataset and performs worst (13 F1 below an ELMo baseline) on QuAC \cite{choi2018quac} a dataset which requires modeling structured dialog acts and answer span selections of teacher-student interactions. On DROP \cite{dua2019drop}, a dataset testing discrete reasoning and numeracy in the context of reading comprehension, GPT-3 in a few-shot setting outperforms the fine-tuned BERT baseline from the original paper but is still well below both human performance and state-of-the-art approaches which augment neural networks with symbolic systems \cite{ran2019numnet}. On SQuAD 2.0 \cite{rajpurkar2018know}, GPT-3 demonstrates its few-shot learning capabilities, improving by almost 10 F1 (to 69.8) compared to a zero-shot setting. This allows it to slightly outperform the best fine-tuned result in the original paper. On RACE \cite{lai2017race}, a multiple choice dataset of middle school and high school english examinations, GPT-3 performs relatively weakly and is only competitive with the earliest work utilizing contextual representations and is still 45\% behind SOTA.
