% In this work we do not optimize for performance on any specific downstream task. Thus in collecting training data for GPT-3, we use the unfiltered distribution of languages reflected in internet text datasets (primarily Common Crawl). As a result, although GPT-3's training data primarily consists of English (93\% by word count), it also includes 7\% non-English content. These languages are documented in the \href{https://github.com/openai/gpt-3}{supplemental material}.  GPT-2 \cite{radford2019language} previously found that a dataset with a very small fraction of non-English content could lead to promising initial results on translation in the few-shot setting, but was not competitive with existing unsupervised machine translation approaches.  Here we test the extent to which GPT-3 can improve these abilities via greater capacity and a larger fraction of non-English languages in its training data.

For GPT-2 a filter was used on a multilingual collection of documents to produce an English only dataset due to capacity concerns. Even with this filtering GPT-2 showed some evidence of multilingual capability and performed non-trivially when translating between French and English despite only training on 10 megabytes of remaining French text. Since we increase the capacity by over two orders of magnitude from GPT-2 to GPT-3, we also expand the scope of the training dataset to include more representation of other languages, though this remains an area for further improvement. As discussed in \ref{section:Training Dataset} the majority of our data is derived from raw Common Crawl with only quality-based filtering. Although GPT-3's training data is still primarily English (93\% by word count), it also includes 7\% of text in other languages. These languages are documented in the \href{https://github.com/openai/gpt-3}{supplemental material}. In order to better understand translation capability, we also expand our analysis to include two additional commonly studied languages, German and Romanian.

Existing unsupervised machine translation approaches often combine pretraining on a pair of monolingual datasets with back-translation \cite{sennrich2015improving} to bridge the two languages in a controlled way. By contrast, GPT-3 learns from a blend of training data that mixes many languages together in a natural way, combining them on a word, sentence, and document level. GPT-3 also uses a single training objective which is not customized or designed for any task in particular. However, our one / few-shot settings aren't strictly comparable to prior unsupervised work since they make use of a small amount of paired examples (1 or 64). This corresponds to up to a page or two of in-context training data. 


\input{tables/translation.tex}
\input{graphs/translation.tex}
    

Results are shown in Table \ref{table:translation}. Zero-shot GPT-3, which only receives on a natural language description of the task, still underperforms recent unsupervised NMT results. However, providing only a single example demonstration for each translation task improves performance by over 7 BLEU and nears competitive performance with prior work. GPT-3 in the full few-shot setting further improves another 4 BLEU resulting in similar average performance to prior unsupervised NMT work. GPT-3 has a noticeable skew in its performance depending on language direction. For the three input languages studied, GPT-3 significantly outperforms prior unsupervised NMT work when translating into English but underperforms when translating in the other direction. Performance on En-Ro is a noticeable outlier at over 10 BLEU worse than prior unsupervised NMT work. This could be a weakness due to reusing the byte-level BPE tokenizer of GPT-2 which was developed for an almost entirely English training dataset. For both Fr-En and De-En, few shot GPT-3 outperforms the best supervised result we could find but due to our unfamiliarity with the literature and the appearance that these are un-competitive benchmarks we do not suspect those results represent true state of the art. For Ro-En, few shot GPT-3 performs within 0.5 BLEU of the overall SOTA which is achieved by a combination of unsupervised pretraining, supervised finetuning on 608K labeled examples, and backtranslation \cite{liu2019multi}.

Finally, across all language pairs and across all three settings (zero-, one-, and few-shot), there is a smooth trend of improvement with model capacity.  This is shown in Figure \ref{graph:translation} in the case of few-shot results, and scaling for all three settings is shown in Appendix \ref{appendix:results_on_all_tasks}.

